Coherent optical association of a single molecule

### 2020-10-15 paper.tex
White space, regenerate PDF

\begin{document}
\title{Coherent optical association of a single molecule}
\author{Yichao Yu}
\email{yichaoyu@g.harvard.edu}
\cuaphysics
\author{Kenneth Wang}
\cuaphysics
\author{Jonathan~D.~Hood}
\affiliation{Department of Chemistry, Purdue University, West Lafayette, Indianna, 47906}
\author{Lewis~R.~B.~Picard}
\cuaphysics
\author{Jessie~T.~Zhang}
\cuaphysics
\author{William~B.~Cairncross}
\cuaphysics
\author{Jeremy~M.~Hutson}
\affiliation{Joint Quantum Centre Durham-Newcastle, Department of Chemistry, Durham University, Durham, DH1 3LE, United Kingdom}
\author{Till Rosenband}
\cuaphysics
\author{Kang-Kuen~Ni}
\email{ni@chemistry.harvard.edu}
\cuaphysics
%\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts 02138, USA}
%\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
%\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts 02138, USA}

@@

>>>>

\begin{document}
\title{Coherent optical association of a single molecule}
\author{Yichao~Yu}
\email{yichaoyu@g.harvard.edu}
\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts 02138, USA}
\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts 02138, USA}
\author{Kenneth~Wang}
\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts 02138, USA}
\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts 02138, USA}
\author{Jonathan~D.~Hood}
\affiliation{Department of Chemistry, Purdue University, West Lafayette, Indianna, 47906}
\author{Lewis~R.~B.~Picard}
\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts 02138, USA}
\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts 02138, USA}

\author{Jessie~T.~Zhang}
\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts 02138, USA}
\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts 02138, USA}

\author{William~B.~Cairncross}
\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts 02138, USA}
\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts 02138, USA}

\author{Jeremy~M.~Hutson}
\affiliation{Joint Quantum Centre Durham-Newcastle, Department of Chemistry, Durham University, Durham, DH1 3LE, United Kingdom}
\author{Till Rosenband}
\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
\author{Kang-Kuen~Ni}
\email{ni@chemistry.harvard.edu}
\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts 02138, USA}
\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts 02138, USA}

% \affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts 02138, USA}
% \affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
% \affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts 02138, USA}

@@

In conclusion, we have formed a weakly bound NaCs molecule in an optical tweezer via an optical Raman transfer. A theoretical investigation including all excited states of $ c^3\Sigma^+(\Omega = 1)$ and coupled channel ground state wavefunctions indicated better transfer efficiency using a deeply bound intermediate state and the $ \ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}} } $ hyperfine state combination. Using these theoretical insights, we located the weakly bound state and coherently associated the atoms into the weakly bound molecule. Our transfer efficiency is limited by an unknown scattering source resulting in measured scattering rates over 10 times larger than theory predictions. Despite this limitation, the transfer efficiency may be further improved by increasing the $ \Omega_a/\Omega_m$ ratio by exploring the possibility of driving to more deeply bound states. There may also be a better choice of single photon detuning to increase the Raman Rabi frequency, since our location results in about 30\% cancellation of the Raman Rabi frequency due to an offset of unknown origin. (Do we want to mention also technical improvements as another way to potentially improve our signal? Though I guess that was mentioned directly in the paragraph above...) Nevertheless, our technique, with the right choice of parameters, can be used to form a more diverse set of molecular species, since it does not rely on a magnetic Feshbach resonance or a narrow excited state (More sentences here to discuss scientific outlook, but without repeating the introduction...? \textcolor{blue}{Yes, on topics related to single molecules for exciting science!!})
